Online Verification of Commutativity

### 2020-10-14 acmPaper/paper.tex
Addressed algorithms stuff

\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
\usepackage{fncylab}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{microtype}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\begin{algorithm}[t]
\label{alg_spanning_set}
\DontPrintSemicolon
\KwResult{Find a spanning set Rs = [$r_1$, ... ,$r_k$].}

Graph existingGraph\;
$R_s$ $\gets$ \{\}\;
\ForEach{node v in V}{
    Subgraph $\gets$ existingGraph.extractReachableSection(v)\;
    Tree $\gets$ createMinimumSpanningTree(Subgraph)\;
    excludedEdges = edges in Subgraph - edges in Tree\;
    \ForEach{edge e $\in$ excludedEdges}{
        firstPath = Tree.findPath(source: e.source, sink: e.sink)\;
        $R_s$.addElement((firstPath, e))\;
    } 
}
\KwRet{$R_s$}\;

@@

\begin{algorithm}[t]
\DontPrintSemicolon
\KwResult{Find a minimal spanning set of path pairs (bilinkings) R.}

\SetKwFunction{FSigma}{$\sigma$}
\SetKwProg{Fn}{Function}{:}{}
\Fn{\FSigma{input set S, spanning set Rs}}{
    output $\gets$ \{\}\;
    \For{bilinking $\in$ Rs}{
        \tcc{Get fragments that could build up to the bilinking. Corresponds to applying <> function.}
        smallerPairs $\gets$ allShorterPieces(bilinking)\;
        consideredPieces $\gets$ smallerPairs $\cap$ S \;
        \tcc{Now see if bilinking can be built from these pieces.}
        \If{linearlyDependent(consideredPieces, bilinking)}{
            output.add(bilinking)\;
        }
    }
    \KwRet{output}
}

@@

\begin{algorithm}[t]
\DontPrintSemicolon
\KwData{existing graph, new edge.}
\KwResult{Set of parallel pairs to verify.}
\SetKwProg{try}{try}{:}{}
\SetKwProg{catch}{catch}{:}{end}
Graph existingGraph;
Edge newEdge;

parallelPairs $\gets$ \{\}\;
\For{src in existingGraph.Nodes}{
    \For{snk in existingGraph}{
        \try{}{
            Path pathWithNewEdge $\gets$ FindPath(
                % graph: existingGraph, 
                sourceNode: src,
                sinkNode: newEdge.Source +\;
            newEdge as Path +\;
            FindPath(
                % graph: exisingGraph, 
                sourceNode: newEdge.Sink, 
                sinkNode: snk)\;
            \If{src == snk}{
                pathInOldGraph $\gets$ identity(src)\;
            }
            \Else(){
                Path pathInOldGraph $\gets$ FindPath(
                    % graph: existingGraph, 
                    sourceNode: src, 
                    sinkNode: snk)\;
            }
            parallelPairs.add((pathInOldGraph, pathWithNewEdge))\;
        }
        \catch{PathFindingFailedException}{
           \tcc{No comparable pairs from node src to node snk that need to be checked}
           continue\;
        }
    }
}
\KwRet{parallelPairs}\;
\caption{Online polynomial time algorithm to find parallel pair set.}
\label{algo_online_polynomial}
\end{algorithm}

@@

\begin{algorithm}
\DontPrintSemicolon
\KwData{Existing graph, new edge.}
\KwResult{Set of parallel pairs to verify.}
Graph existingGraph\;
Edge (S, T)\;

@@

verificationSet $\gets$ \{\}\;
\While{terminalPairGraph.nodes not empty}{
    currentNode $\gets$ terminalPairGraph.node\;
    \tcp*{an arbitrarily chosen node of terminalPairGraph}
    \While{currentNode has predecessors}{
        currentNode $\gets$ predecessor\;
        \tcp*{an arbitrarily chosen predecessor of current Node}
    }
    verificationSet.add(currentNode)\;
    terminalPairGraph.removeAllSuccessors(currentNode)\;
}
\KwRet{verificationSet}\;
\caption{Minimal set finding algorithm.}
\label{algo_online_minimal}
\end{algorithm}

@@

\begin{figure}
    % TODO format nicely.
    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_OptimalSet.pdf}
      \caption{~\ref{algo_online_minimal}.}
      \label{fig:sfigOptimalTvsS}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_Polynomial.pdf}
      \caption{~\ref{algo_online_polynomial}.}
      \label{fig:sfigPolynomialTvsS}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_NaiveChecker.pdf}
      \caption{Naive baseline.}
      \label{fig:sfigNa\"{i}veTvsS}
    \end{subfigure}

\end{figure}
\begin{figure}\ContinuedFloat

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_TwoFlipPathChecker.pdf}
      \caption{Two flip tolerant baseline.}
      \label{fig:sfigTwoFlipTvsS}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_BatchChecker.pdf}
      \caption{Batch algorithm baseline.}
      \label{fig:sfigBatchTvsS}
    \end{subfigure}
    \caption{Plots of scaling of time with input size and density.}
    \label{fig:timeVsSize}
\end{figure}

>>>>

\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
\usepackage{fncylab}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{microtype}
\usepackage{float}
% \usepackage{endfloat}
% \usepackage{afterpage}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\begin{algorithm}[tb]
\label{alg_spanning_set}
\DontPrintSemicolon
\KwResult{Find a spanning set Rs = [$r_1$, ... ,$r_k$].}

Graph existingGraph\;
$R_s$ $\gets$ \{\}\;
\ForEach{node v in V}{
    subgraph $\gets$ existingGraph.extractReachableSection(v)\;
    \tcc{Get the portion of the graph that can be reached starting from v.}
    tree $\gets$ createMinimumSpanningTree(subgraph)\;
    excludedEdges = edges in subgraph - edges in tree\;
    \ForEach{edge e $\in$ excludedEdges}{
        firstPath = tree.findPath(source: e.source, sink: e.sink)\;
        $R_s$.addElement((firstPath, e))\;
    } 
}
\KwRet{$R_s$}\;

@@

\begin{algorithm}[tb]
\DontPrintSemicolon
\KwResult{Find a minimal spanning set of path pairs (bilinkings) R.}

\SetKwFunction{FSigma}{$\sigma$}
\SetKwProg{Fn}{Function}{:}{}
\Fn{\FSigma{input set S, spanning set Rs}}{
    output $\gets$ \{\}\;
    \For{bilinking $\in$ Rs}{
        smallerPairs $\gets$ allShorterPieces(bilinking)\;
        \tcc{Get fragments that could build up to the bilinking. Corresponds to applying <> function.}
        consideredPieces $\gets$ smallerPairs $\cap$ S \;
        \tcc{Now see if bilinking can be built from these pieces.}
        \tcc{Linear independence is in GF(2) as in algorithm description.}
        \If{linearlyDependent(consideredPieces, bilinking)}{
            output.add(bilinking)\;
        }
    }
    \KwRet{output}
}

@@

\begin{algorithm}[tb]
\DontPrintSemicolon
\KwData{existing graph, new edge.}
\KwResult{Set of parallel pairs to verify.}
\SetKwProg{try}{try}{:}{}
\SetKwProg{catch}{catch}{:}{end}
Graph existingGraph;
Edge newEdge;

parallelPairs $\gets$ \{\}\;
\For{src in existingGraph.Nodes}{
    \For{snk in existingGraph}{
        \try{}{
            \tcc{Use any standard path finding algorithm such as BFS to find a path in the existing graph from the specified source to sink.}
            Path pathWithNewEdge $\gets$ FindPath(
                % graph: existingGraph, 
                sourceNode: src,
                sinkNode: newEdge.Source) +\;
            newEdge +\;
            FindPath(
                % graph: exisingGraph, 
                sourceNode: newEdge.Sink, 
                sinkNode: snk)\;
            \If{src == snk}{
                \tcc{Assign the nullary path from src to snk.}
                pathInOldGraph $\gets$ src\;
            }
            \Else(){
                Path pathInOldGraph $\gets$ FindPath(
                    % graph: existingGraph, 
                    sourceNode: src, 
                    sinkNode: snk)\;
            }
            parallelPairs.add((pathInOldGraph, pathWithNewEdge))\;
        }
        \catch{PathFindingFailedException}{
           \tcc{No comparable pairs from node src to node snk that need to be checked}
           continue\;
        }
    }
}
\KwRet{parallelPairs}\;
\caption{Online polynomial time algorithm to find parallel pair set.}
\label{algo_online_polynomial}
\end{algorithm}

@@

\begin{algorithm}[tb]
\DontPrintSemicolon
\KwData{Existing graph, new edge.}
\KwResult{Set of parallel pairs to verify.}
Graph existingGraph\;
Edge (S, T)\;

@@

verificationSet $\gets$ \{\}\;
\While{terminalPairGraph.nodes not empty}{
    currentNode $\gets$ terminalPairGraph.node\;
    \tcp*{an arbitrarily chosen node of terminalPairGraph}
    \While{currentNode has predecessors}{
        currentNode $\gets$ predecessorOfCurrentNode\;
        \tcp*{an arbitrarily chosen predecessor of current Node}
    }
    verificationSet.add(currentNode)\;
    terminalPairGraph.removeAllSuccessors(currentNode)\;
}
\KwRet{verificationSet}\;
\caption{Minimal set finding algorithm.}
\label{algo_online_minimal}
\end{algorithm}

@@

\begin{figure*}
    % TODO format nicely.
    \begin{subfigure}{0.3\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_OptimalSet.pdf}
      \caption{~\ref{algo_online_minimal}.}
      \label{fig:sfigOptimalTvsS}
    \end{subfigure}
    ~
    \begin{subfigure}{0.3\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_Polynomial.pdf}
      \caption{~\ref{algo_online_polynomial}.}
      \label{fig:sfigPolynomialTvsS}
    \end{subfigure}
    ~
    \begin{subfigure}{0.3\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_NaiveChecker.pdf}
      \caption{Naive baseline.}
      \label{fig:sfigNa\"{i}veTvsS}
    \end{subfigure}

    ~
% \end{figure}
% \begin{figure}\ContinuedFloat

    \begin{subfigure}{0.3\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_TwoFlipPathChecker.pdf}
      \caption{Two flip tolerant baseline.}
      \label{fig:sfigTwoFlipTvsS}
    \end{subfigure}
    ~
    \begin{subfigure}{0.3\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_BatchChecker.pdf}
      \caption{Batch algorithm baseline.}
      \label{fig:sfigBatchTvsS}
    \end{subfigure}
    \caption{Plots of scaling of time with input size and density.}
    \label{fig:timeVsSize}
\end{figure*}
